Software Citation Principles

### 2016-03-02 sc-principles/software-citation-principles.tex
Updates from ShareLaTeX

The following set of software citation principles were originally based on an adaptation of the parallel set of data citation principles~\cite{data-citation-principles}, and then were modified based on working group discussions and the information from the use cases and the related work.

\begin{enumerate}
\item \textbf{Importance}:
Software should be considered a legitimate, citable product of research. Software citations should be accorded the same importance in the scholarly record as citations of other research objects, such as publications and data. Software should be cited whenever and wherever a research product (such as a paper) relies upon it, specifically, as part of the standard reference list for that research product.
\item \textbf{Credit and Attribution}
Software citations should facilitate giving scholarly credit and normative and legal attribution to all contributors to the software, recognizing that a single style or mechanism of attribution may not be applicable to all software.\scnote{At least four styles (AMS, APA, Chicago, MLA) for software citation are illustrated with examples in ~\cite{lipson2011cite}.}
\item \textbf{Unique Identification}
A software citation should include a method for identification that is machine actionable, globally unique, and widely used by a community.
\item \textbf{Persistence}
Unique identifiers, and metadata describing the software, and its disposition, should persist -- even beyond the lifespan of the software they describe.
\item \textbf{Accessibility}
Software citations should facilitate access to the software themselves and to such associated metadata, documentation, data, and other materials, as are necessary for both humans and machines to make informed use of the referenced software.\dmnote{Should provide a location where the software is available. Should we say anything about environments?}
\item \textbf{Specificity and Verifiability}
Software citations should facilitate identification of, access to, and verification of the specific software that support a claim. Citations or citation metadata should include information about provenance and fixity sufficient to facilitate verifying that the specific version and/or portion of software retrieved subsequently is the same as was originally cited.
\item \textbf{Interoperability and Flexibility}
Software citation methods should be sufficiently flexible to accommodate the variant practices among communities, but should not differ so much that they compromise interoperability of software citation practices across communities.
\end{enumerate}

>>>>

\katznote{The current content of this section is liberally borrowed and loosely adapted from \cite{data-citation-principles}.  We we will want to add some text here explaining that we started with that document, and then modified it to take into account the information from the use cases and the related work, once we do so.}

\begin{enumerate}
\item \textbf{Importance}:
Software should be considered a legitimate, citable product of research. Software citations should be accorded the same importance in the scholarly record as citations of other research objects, such as publications and data. Software should be cited whenever and wherever a research product (such as a paper) relies upon it, specifically, as part of the standard reference list for that research product.
\item \textbf{Credit and Attribution}
Software citations should facilitate giving scholarly credit and normative and legal attribution to all contributors to the software, recognizing that a single style or mechanism of attribution may not be applicable to all software.\scnote{At least four styles (AMS, APA, Chicago, MLA) for software citation are illustrated with examples in ~\cite{lipson2011cite}.}
\item \textbf{Unique Identification}
A software citation should include a persistent method for identification that is machine actionable, globally unique, and widely used by a community.
\item \textbf{Persistence}
Unique identifiers, and metadata describing the software, and its disposition, should persist -- even beyond the lifespan of the software they describe.
\item \textbf{Accessibility}
Software citations should facilitate access to the software itself and to such associated metadata, documentation, data, and other materials, as are necessary for both humans and machines to make informed use of the referenced software.\dmnote{Should provide a location where the software is available. Should we say anything about environments?}
\item \textbf{Specificity and Verifiability}
Software citations should facilitate identification of, access to, and verification of the specific software that support a claim. Citations or citation metadata should include information about provenance and fixity sufficient to facilitate verifying that the specific version and/or portion of software retrieved subsequently is the same as was originally cited.
\item \textbf{Interoperability and Flexibility}
Software citation methods should be sufficiently flexible to accommodate the variant practices among communities, but should not differ so much that they compromise interoperability of software citation practices across communities.
\end{enumerate}
\dmnote{ Anything missing? Configurations? Interactive software? Screenshots? \ldots ?}
